---
title: "Twitter Scrapping"
author: "Justin Ho"
date: "11/12/2017"
output:
  html_document:
    keep_md: true
    self_contained: true
---

## Getting Twitter API Key
To access the Twitter APIs, you will need to register a twitter application. To register a twitter application and get your consumer keys:

1. Go to [Twitter's App Page](https://apps.twitter.com) in a web browser.
2. Click on 'create new app'.
3. Give your app a unique name, a description, any relevant web address, and agree to the terms and conditions. Set the callback URL to http://127.0.0.1:1410. You might have to add a cellphone number your twitter account.
4. Go to the keys and access section of the app page, and copy your consumer key and consumer secret to the code below.
5. (optional): For actions requiring write permissions, generate an access token and access secret.
(Drafted by Ken Benoit)

You will also need to install at least the following R packages:
```{r, eval = FALSE}
install.packages(c('twitteR', 'RCurl', 'ROAuth', 'httr'))
```


For security purpose, the keys is stored in another R file, don't upload this onto Github!
```{r}
require(twitteR)

source("twitterkeys.R")
setup_twitter_oauth(consumerKey, consumerSecret, accessToken, accessSecret)
```


Try to search tweets about "#MeToo" and turn into dataframe
```{r}
results <- searchTwitter('#metoo', n=100)
twdf <- as.data.frame(t(sapply(results, as.data.frame)))
```


Have a quick preview
```{r}
head(twdf$text)
```

